Path Analysis Data Development - Chapter 2

### 2016-10-31 sem-data-development.Rmd
Add newline.

## Join remotely sensed and derived physical data
LiDAR products, variables derived from DEMs
```{r join remotely sensed data}
plots_env <- inner_join(plots_env, plots_vegtopo, by = "PLOT_ID")
summary(plots_env)
plots_env$elev_m <- plots_env$elev15m * .3048
# plots_env <- select(plots_env, -elevation, -tmi) #remove elevation, tmi from old derivation (I think a legacy 10m USGS DEM)
plots_env$veght_m <- plots_env$veght15m * .3048
plots_env <- select(plots_env, -elevation, -elev15m, -veght15m, -tmi) %>% 
      rename(plotid = PLOT_ID)
plots_env$plotid <- tolower(plots_env$plotid)
rm(plots_vegtopo)
```

@@

Examine temperature data, which is in long format and covers sample years 2004 through 2014. This means that I will need to exclude disease-related sampling from 2003 of the ecological data (NAs should fill-in if missing data when joining).
```{r examine temperature & rain data}
# Temperature Data
summary(rs_temps)
rs_temps$plotid <- tolower(rs_temps$plotid)
summary(summer_temps)
summer_temps$plotid <- tolower(summer_temps$plotid)

>>>>

## Join remotely sensed and derived physical data
LiDAR products, variables derived from DEMs

```{r join remotely sensed data}
plots_env <- inner_join(plots_env, plots_vegtopo, by = "PLOT_ID")
summary(plots_env)
plots_env$elev_m <- plots_env$elev15m * .3048
# plots_env <- select(plots_env, -elevation, -tmi) #remove elevation, tmi from old derivation (I think a legacy 10m USGS DEM)
plots_env$veght_m <- plots_env$veght15m * .3048
plots_env <- select(plots_env, -elevation, -elev15m, -veght15m, -tmi) %>% 
      rename(plotid = PLOT_ID)
plots_env$plotid <- tolower(plots_env$plotid)
rm(plots_vegtopo)
```

@@

Examine temperature data, which is in long format and covers sample years 2004 through 2014. This means that I will need to exclude disease-related sampling from 2003 of the ecological data (NAs should fill-in if missing data when joining).

```{r examine temperature & rain data}
# Temperature Data
summary(rs_temps)
rs_temps$plotid <- tolower(rs_temps$plotid)
summary(summer_temps)
summer_temps$plotid <- tolower(summer_temps$plotid)
